%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{NGUYEN HUU TRUONG} % Your name 
\address{Ho Chi Minh City, Vietnam} % Your address 
\address{+84 986103378 \\ truongnh2802@gmail.com} % Your phone number and email
\address{https://www.linkedin.com/in/truongnh28}
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Objective}

%     As a recently graduated Software Engineer with a strong foundation in programming, data structures, algorithms, and systems, I am eager to apply my skills and knowledge to develop efficient, scalable, and secure backend software systems. I am a quick learner, adaptable to new environments, and a team player who is committed to completing projects to the best of my ability. I am also passionate about gaining real-world experience, enhancing my technical skills, and becoming an expert Backend Software Engineer who can contribute to the company's growth.

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    {\bf Ho Chi Minh City University of Technology (HCMUT)} \hfill {Dec 2024 -- Present}
    \\
    Master of Engineering in Data Science, GPA: 3.31/4.00

    {\bf Posts and Telecommunications Institute of Technology (PTIT)} \hfill {Sep 2019 -- Jun 2024}
    \\
    Engineer's Degree in Information Technology, GPA: 3.31/4.00

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

    \begin{rSubsection}{Zalopay - VNG Corporation}{Aug 2022 -- Present}{Software Engineer}{Ho Chi Minh City}
        \item \textbf{CI/CD:} Designed and implemented a Kubernetes-based CI/CD platform that automates the full delivery pipeline from code commit to production deployment. Achieved an average pipeline build time of 5 minutes, integrated code quality gates (SonarQube) and security scanning to enforce engineering standards, significantly reduced human errors in the release process, and improved overall deployment frequency and developer productivity.
        \item \textbf{Gateway:} Designed and implemented the Ratelimit platform (based on Apisix), enabling developers to configure and enforce rate-limiting policies within minutes. Built the CAS platform — a centralized authentication system securing all internal ZaloPay tools, significantly improving system security posture.
        \item \textbf{Private Cloud (SaaS):} Participated in researching and implementing a private cloud platform based on Kubernetes. Contributed to a self-service infrastructure provisioning system that automates resource creation for Redis, Kafka, MySQL, Etcd clusters, and other resources, reducing provisioning time from several days to 5 minutes and enabling development teams to deploy and scale independently.
        \item \textbf{Innovation:} Actively participated in R\&D initiatives. Researched and provided an OCR-based solution for the customer support team, transforming the user support flow from manual to automated — reducing processing time by 99\% from 20 minutes to under 1 minute per case.
        \item \textbf{Mentoring \& Knowledge Sharing:} Mentored junior engineers through technical challenges, code reviews, and onboarding. Organized monthly knowledge-sharing sessions and actively pursued continuous learning through internal courses and external platforms.

    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Zalopay - VNG Corporation}{May 2022 -- Aug 2022}{Fresher Software Engineer}{Ho Chi Minh City}

        \item \textbf{Competitive Selection:} Selected from over 2000 applicants in the VNG Tech Program 2022 through a rigorous process including technical entrance tests and mentor interviews.
        \item \textbf{Structured Training:} Completed a comprehensive mentorship program covering backend engineering, databases, distributed systems, and front-end development, alongside soft skills including teamwork and technical communication.

    \end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
%	PROJECTS
%-------------------------------------------------------------------------------

\begin{rSection}{Projects}

    \begin{rSubsection}{CI/CD Platform}{Oct 2024 -- Present}{Maintainer}{}
        \item Maintainer of ZaloPay's internal CI/CD platform built on Kubernetes, automating the full software delivery pipeline from source code to production deployment.
        \item Designed and implemented pipeline orchestration workflows that reduced deployment time and minimized human error across development teams.
        \item Integrated code quality gates (SonarQube), automated testing, and security scanning into the pipeline to enforce engineering standards.
        \item \textbf{Technologies:} Golang, Jenkins, Kubernetes, SonarQube, GitLab CI
    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Gateway Ecosystem (Platform SSO \& Ratelimit)}{Sep 2023 -- Present}{Owner}{}
        \item Designed and owned the Zalopay authentication system — a centralized, dynamically configurable authentication layer securing all internal ZaloPay tools and services.
        \item Built the ZaloPay Ratelimit service on top of the Apisix ecosystem, enabling developers to define and enforce rate-limiting policies within minutes via self-service configuration.
        \item Improved overall API gateway performance and security posture across the platform.
        \item \textbf{Technologies:} Golang, MySQL, Redis, Apisix, Plugin architecture
    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Gears - Private Cloud Provider}{Aug 2022 -- Present}{Maintainer}{}
        \item Maintained and extended Zalopay Gears, a self-service infrastructure provisioning platform that automates resource creation for Kafka topics, MySQL clusters, Redis sentinel/cluster, Etcd clusters.
        \item Contributed to reducing infrastructure setup time for development teams from days to minutes by leveraging Kubernetes Operators and workflow automation.
        \item Collaborated on implementing Temporal-based workflows to ensure reliability and observability of provisioning operations.
        \item \textbf{Technologies:} Golang, MySQL, Kubernetes, Kubernetes Operator, Temporal
    \end{rSubsection}

    %------------------------------------------------

    \begin{rSubsection}{Customer Service AI Application}{Jan 2025 -- Present}{Owner}{}
        \item Designed and built an AI-powered customer service application leveraging Large Language Models (LLMs) and Retrieval-Augmented Generation (RAG) to provide accurate, context-aware responses to user queries.
        \item Implemented a knowledge base pipeline for document ingestion, embedding, and semantic retrieval to ground LLM responses in real company data.
        \item Owned the end-to-end architecture including backend API, LLM integration, and retrieval system design.
        \item \textbf{Technologies:} Python, LLM, RAG
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Programming Languages       & Golang, Python.                                              \\
        Data Structure \& Algorithm & Experience in problem solving                                \\
        Databases                   & MySQL (Percona), Redis, Etcd                                 \\
        Technologies                & Docker, Kubernetes, Apisix, Kubernetes Operator              \\
        Version Control             & Git, Gitlab                                                  \\
        Self-study                  & Open-source experience, able to read and write clean English \\
                                    & documents, Research and Development (R\&D)                   \\
        Methodology                 & Familiarity with Agile/Scrum                                 \\
    \end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS & AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards} \itemsep -3pt
    \textbf{Champion at Zalopay Hackathon 2025, Zalopay CTF 2025} \hfill 2025 \\
    \textbf{2nd Runner-up in Zalopay Hackathon 2023} \hfill 2023 \\
    \textbf{Second Prize in PTIT ICPC} \hfill 2022 \\
    \textbf{Participate in The 2021 ACM/ICPC Vietnam Regional Contest} \hfill 2022 \\
\end{rSection}

%----------------------------------------------------------------------------------------
%	VOLUNTEER SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Volunteer}

%     \begin{rSubsection}{Information Technology Multimedia Club}{Jan 2020 -- Present}{Technical Consultant}{HCMC}

%         As a technical consultant for the club, I am responsible for:

%         \item \textbf{Organizing:} Support in organizing club activities.
%         \item \textbf{Mentoring:} Guiding, developing, and mentoring club members to achieve their full potential.
%         \item \textbf{Instructor:} Instructor and teaching assistant for C++ programming language class, basic algorithm class,... with more than 30 members.

%     \end{rSubsection}

% \end{rSection}

\end{document}
